---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(width = 60, digits = 3)
```

# miceds

## Multivariate Imputation by Chained Equations for DataSHIELD

The [`mice`](https://github.com/stefvanbuuren/mice) package
implements a popular method to deal with missing data. The package creates
multiple imputations (replacement values) for multivariate missing
data.

The [`DataSHIELD`](https://github.com/datashield) framework is a 
platform for federated data analysis that brings the algorithm to
the data. 

The [`miceds`](https://github.com/stefvanbuuren/miceds) package is an add-on to `mice` that makes multiple 
imputation available for federated data systems.

## Installation

If you have been marked as a collaborator on GitHub, you need to generate a personal access token (PAT) on <https://github.com/settings/tokens>. The following code installs the `miceds` package:

```{r eval = FALSE}
install.packages("devtools")
Sys.setenv(GITHUB_PAT = "copy_your_token_here")
devtools::install_github("stefvanbuuren/miceds")
```

Note: It is best to put your token in [`.Renviron`](http://happygitwithr.com/github-pat.html#how-do-you-authenticate-yourself).

## Note

Warning: This is an experimental feature. These function do not yet actually work. If you have ideas about the integration of `mice` and `DataSHIELD` feel free to join in. 

## Related initiative

Related work appears in [`dsMice`](https://github.com/gflcampos/dsMice) and 
[`dsMiceClient`](https://github.com/gflcampos/dsMiceClient).

## Minimal example

    Include minimal example here using public DataSHIELD nodes.

