---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(width = 60, digits = 3)
```

# dsMiceClient

## Multivariate Imputation by Chained Equations for DataSHIELD

The [`mice`](https://github.com/stefvanbuuren/mice) package
creates multiple imputations (replacement values) for multivariate 
missing data.

The [`DataSHIELD`](https://github.com/datashield) framework is a 
platform for federated data analysis that brings the algorithm to
the data. 

The [`dsMiceClient`](https://github.com/stefvanbuuren/dsMiceClient) package is an 
add-on to `mice` that makes multiple imputation available for federated data systems.

## Installation

The following code installs the `dsMiceClient` package:

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("stefvanbuuren/dsMiceClient")
```

In order to work well, the `DataSHIELD` nodes should have installed the server site functions available from 
[`dsMice`](https://github.com/stefvanbuuren/dsMice)

## Note

Warning: This is an experimental feature. These function do not yet actually work. If you have ideas about the integration of `mice` and `DataSHIELD` feel free to join in. 

## Related initiative

Related work appears in [`dsMice`](https://github.com/gflcampos/dsMice) and 
[`dsMiceClient`](https://github.com/gflcampos/dsMiceClient).

## Minimal example

    Include minimal example here using public DataSHIELD nodes.

